Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-29 WSSSPE4_report/WSSSPE4_report.tex
adding ORCID
adding partial affil info

%
\thanks{{}$^{(1)}$ National Center for Supercomputing Applications (NCSA) \&
Department of Computer Science  \&
Department of Electrical and Computer Engineering  \&
School of Information Sciences (iSchool),
University of Illinois, Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: 0000-0003-4425-7097}
%
\thanks{{}$^{(3)}$ Center for Research Computing \& Department of Computer Science and Engineering,
University of Notre Dame, IN, USA; sandra.gesing@nd.edu; ORCID: 0000-0002-6051-0673}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: ?}
%
\thanks{{}$^{(5)}$ The Software Sustainability Institute, Southampton, UK; s.hettrick@software.ac.uk; ORCID: 0000-0002-6809-5195}
%
\thanks{{}$^{(6)}$ Astrophysics Source Code Library, Astronomy Department, University of Maryland, College Park, MD, USA; aallen@ascl.net; ORCID: 0000-0003-3477-2845}
%
\thanks{{}$^{(7)}$ \note{info needed}}
%
\thanks{{}$^{(8)}$ \note{info needed}}
%
\thanks{{}$^{(9)}$ \note{info needed}}
%
\thanks{{}$^{(10)}$ \note{info needed}}
%
\thanks{{}$^{(11)}$ University of California, Berkeley, Berkeley Institute for Data Science (BIDS), Berkeley, CA, USA; stuart@stuartgeiger.com; ORCID: 0000-0001-7215-0532}
%
\thanks{{}$^{(12)}$ Perimeter Institute for Theoretical Physics \&
Department of Physics, University of Guelph, 
Guelph, ON, Canada; 
jmiller@perimeterinstitute.ca; ORCID: 0000-0001-6432-7860}
%
\thanks{{}$^{(13)}$ \note{info needed}}
%
\thanks{{}$^{(14)}$ Department of Mathematics, Colorado State
  University, Fort Collins, CO 80523, USA; bangerth@colostate.edu; ORCID: 0000-0003-2311-9402}

>>>>

%
\thanks{{}$^{(1)}$ National Center for Supercomputing Applications (NCSA) \&
Department of Computer Science  \&
Department of Electrical and Computer Engineering  \&
School of Information Sciences (iSchool),
University of Illinois, Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: 0000-0003-4425-7097}
%
\thanks{{}$^{(3)}$ Center for Research Computing \& Department of Computer Science and Engineering,
University of Notre Dame, IN, USA; sandra.gesing@nd.edu; ORCID: 0000-0002-6051-0673}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: 0000-0002-1021-3101}
%
\thanks{{}$^{(5)}$ The Software Sustainability Institute, Southampton, UK; s.hettrick@software.ac.uk; ORCID: 0000-0002-6809-5195}
%
\thanks{{}$^{(6)}$ Astrophysics Source Code Library, Astronomy Department, University of Maryland, College Park, MD, USA; aallen@ascl.net; ORCID: 0000-0003-3477-2845}
%
\thanks{{}$^{(7)}$ \note{info needed}}
%
\thanks{{}$^{(8)}$ \note{info needed}}
%
\thanks{{}$^{(9)}$ \note{info needed}}
%
\thanks{{}$^{(10)}$ \note{info needed}}
%
\thanks{{}$^{(11)}$ University of California, Berkeley, Berkeley Institute for Data Science (BIDS), Berkeley, CA, USA; stuart@stuartgeiger.com; ORCID: 0000-0001-7215-0532}
%
\thanks{{}$^{(12)}$ Perimeter Institute for Theoretical Physics \&
Department of Physics, University of Guelph, 
Guelph, ON, Canada; 
jmiller@perimeterinstitute.ca; ORCID: 0000-0001-6432-7860}
%
\thanks{{}$^{(13)}$ University of Illinois at Urbana-Champaign, USA; echen35@illinois.edu; ORCID: \note{info needed}}
%
\thanks{{}$^{(14)}$ Department of Mathematics, Colorado State
  University, Fort Collins, CO 80523, USA; bangerth@colostate.edu; ORCID: 0000-0003-2311-9402}
